Internal models of type theory and internal higher categories for the Univalent Foundations

### 2014-03-19 article-models-tt.tex
added a sentence
new section title

\section{Type theory before type constructors}\label{tt}
In this section we give a description of dependent type theory before type
constructors with explicit operations of extension, weakening and substitution. We will
formulate the type theory in such a way that contexts aren't defined
to be lists of variable
declarations. We rather take a syntactic approach in our treatment of contexts,
axiomatizing only what you can do with them and allowing for the freedom to
interpret the axiom in any desired way. 
The main reason is that we don't see variable declarations in the internal
models either. This way we also set out to a more algebraic approach of type
theory and higher category theory. Thirdly, we will not have to be burdened with
superficial comments about variables being bounded or not, or fresh or free or 
not occuring at all.

@@

Besides contexts, families and terms there will also be a notion of `type in
a context'. Only a family of contexts over a context $\Gamma$ is eligible to
be a type in the context $\Gamma$ and we have the intuition that `being a type'
expresses the property of `being an atomic or irreducible family of contexts'.

>>>>

\section{Operational syntactics for type theory before type constructors}\label{tt}
In this section we give a description of dependent type theory before type
constructors with explicit operations of extension, weakening and substitution. We will
formulate the type theory in such a way that contexts aren't defined
to be lists of variable
declarations. We rather take a syntactic approach in our treatment of contexts,
axiomatizing only what you can do with them and allowing for the freedom to
interpret the axiom in any desired way. 
The main reason is that we don't see variable declarations in the internal
models either. This way we also set out to a more algebraic approach of type
theory and higher category theory. Thirdly, we will not have to be burdened with
superficial comments about variables being bounded or not, or fresh or free or 
not occuring at all.

@@

Besides contexts, families and terms there will also be a notion of `type in
a context'. Only a family of contexts over a context $\Gamma$ is eligible to
be a type in the context $\Gamma$ and we have the intuition that `being a type'
expresses the property of `being an atomic or irreducible family of contexts'.
We will not axiomatize that every context is either judgmentally equal to the
empty context or judgmentally equal to the extension of a context by a type,
although it is certainly worth investigating the class of contexts which fall
under this category.
